Leveraging Semantics for a Deep Web Question and Answering System

### 2010-03-01 paper/semsearch10/paper.tex
latest changes

\documentclass{www2010-submission}
\begin{document}

\title{Leveraging Semantics for a Deep Web Question and Answering System} 
\numberofauthors{7}
\author{
	\alignauthor Christan Grant\\
	\email{cgrant@cise.ufl.edu}

	\alignauthor Clint P. George\\
	\email{clintpg@gmail.com}

	\alignauthor Joseph N. Wilson\\
	\email{jnw@cise.ufl.edu}

	\alignauthor Peter J. Dobbins\\
	\email{pjd@cise.ufl.edu}

	\alignauthor Jeff T. Depree\\
	\email{jepree@cise.ufl.edu}

	\alignauthor Christopher A. Shields\\
	\email{cshields@cise.ufl.edu}

	\alignauthor Joir-dan Gumbs\\
	\email{jgumbs@cise.ufl.edu}

	\sharedaffiliation
	\affaddr{Department of Computer and Information Science and Engineering }  \\
	\affaddr{University of Florida} \\
	\affaddr{Gainesville, Florida 32611-6120}
}
\date{April 26,2010}

@@

\section{Introduction}
% Christan
- The best way to answer questions is to see/know if a question has been asked before.
- IEEE potentials talks about the the beaten trail.
- Use reuse in the specific domain of question answering
- 
-

@@

Consider the abbreviated Markov blanket for the category Basketball:
\includegraphics[width=4in,height=4in,viewport=0 0 300 300]{abbreviated_basketball_blanket.png}

The subcategories of the category Basketball (… Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams…) can be seen as grabbing information specifc to the category. The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept. The spousal categories are an abstract description of the subcategories.

@@

\begin{algorithmic}
\function BlanketSubjectRetrieval(blanket, maxLevel):
	\for{category in blanket}
		subjectSet.add(grabSubjects(category))
		diff = afterSize - beforeSize;
		\if{ diff \leq \alpha \and category is a subcategory}
			PlusOneMechanism(category, maxLevel)
		\endif
	\endfor
	return subjectSet
\end{algorithmic}

\begin{algorithmic}
\function PlusOneMechanism(category, level)
	plusOneSet = grabPlusOneSubcategories(category)
	\for{ subcategory in plusOneSet do}
		subjectSet.add(grabSubjects(subcategory));
		diff = afterSize - beforeSize
		\if{ diff \leq \alpha \and level \gt 0}
			PlusOneMechanism(subcategory, level - 1);
		\endif
	\endfor
\end{algorithmic}

>>>>

\documentclass{www2010-submission}
\usepackage{algorithm}
\usepackage{algorithmic}
\begin{document}

\title{Leveraging Semantics for a Deep Web Question and Answering System} 
\numberofauthors{1}
\author{
	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
}

\date{April 26,2010}

@@

\section{Introduction}
% Christan
- IEEE potentials article talks discussed the idea of using the beaten trail. To solve problems
- Typical search engines have several repeat queries.
- We believe that treating these repeat visits as special visits will enhance user search experience
- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
- 
-

@@

Consider the abbreviated Markov blanket for the category Basketball:
%\includegraphics[width=1in,height=1in,viewport=0 0 100 100]{abbreviated_basketball_blanket.png}

The subcategories of the category Basketball (... Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category. The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept. The spousal categories are an abstract description of the subcategories.

@@

\begin{algorithm}
\caption{Blanket Subject Retrieval}
\label{alg1}
	\begin{algorithmic}
	\STATE BlanketSubjectRetrieval(blanket, maxLevel):
		\FOR{category c in blanket}
			\STATE subjectSet.add(grabSubjects(c))
			\STATE diff = afterSize - beforeSize
			\IF{ diff \leq \alpha and c is a subcategory}
				\STATE PlusOneMechanism(category, maxLevel)
			\ENDIF
		\ENDFOR
	\STATE return subjectSet
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Plus One Mechanism}
\label{alg2}
	\begin{algorithmic}
	\STATE PlusOneMechanism(category, level)
		\STATE plusOneSet = grabPlusOneSubcategories(category)
		\FOR{ subcategory in plusOneSet}
			\STATE subjectSet.add(grabSubjects(subcategory))
			\STATE diff = afterSize - beforeSize
			\IF{ diff \leq \alpha \and level \gt 0}
				\STATE PlusOneMechanism(subcategory, level - 1);
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}
